Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-05-27 manuscript.Rmd
Fix typos in manuscript

For social cohesion and count of all events, there is a consistent period of above or nearly above chance determinism from the 26th thorugh 46th window (Figure 16). Determinism also shows above or nearly above chance values in window spans 11-16 and 35-37 (Figure 17). For social cohesion and count of positive events, there is a downward trend in RR as the window moves (Figure 18) and determinism stays largely within chance with the exception of windows 13-19. For social cohesion and negative events, there appears to be an extended time period where RR (Figure 11) and DET (Figure 12) were greater than chance, from the 35th through 46th windows. These windows span from May 3rd, 2012 to May 14th, 2012.

@@

### Syria as Source and Target
By adding Syria as a source in the data filtering, the dataset increased in size by 1,690 samples. These additional observations are times where Syria initiated an event with another country. Events initiated by Syria but directed internally within the country were already captured by the target only filtering. The increase in coupling between positive events and social cohesion is thus due to the inclusion of these externally directed events. Though CRQA metrics for count of all and count of negative events with social cohesion were largely unaffected, count of positive events and social cohesion showed significant levels of determinism, number of lines, max line length, and laminarity that were not present in the target filtered data. Given that the Syria during this time was still under Authoritarian rule, the government may have been initiating more positive external events to prevent intervention by other countries or try to cover up what was going on. We believe that the increased coupling of positive events is thus not reflective of actual social cohesion, but happened by chance. The inflation of the number of positive events when including source observations is causing increased coupling, but it is more likely that the Twitter users were using the platform to raise awareness of the violent, internal events that were being inflicted on them by their government officials and armies and not reporting on the positive external events that did not directly affect them or their saftey.
By visual inspection of the recurrence plots (RPs; Figures 3-8), there appears to be a shift in the dynamics of these systems around observation 35, or May 3rd, 2012. To further investigate these local dynamics, we performed a sliding window technique known as windowed cross-recurrence quantification analysis (WCRQA).

## Windowed-Recurrence Quantification Analysis
### Syria as Target
The time period of differing dynamics, from observation 38 through 43, appears to be captured by WCRQA of social cohesion and count of negative events for both RR (Figure 13) and DET (Figure 14). The amount of recurrence and determinism for these periods almost consistently lie above chance, suggesting that the intensity of negative events coincide with the degree of social cohesion found on Twitter, and that these states carry across multiple days in a way that is different from that of chance.
The above-chance levels of determinism and recurrence rate are demonstrating the coupling of social cohesion and counts of all and negative events during times of strife. We can see this string of highly violent events reflected in the mode ICEWS event for each day (Figure 15), where from May 1st, 2020 to May 15th, 2020, the most frequntly occuring event was almost consistently -10, the most violent event in the coding system. These dates directly correlate with the above chance RR and DET metrics for the WCRQA of social cohesion and count of negative events. Furthermore, for WCRQA of social cohesion and positive event count during this time period, DET (Figure 12) was entirely within chance. This supports our hypothesis, as the positive events are seemingly not coupled with the social cohesion on Twitter during civil uprisings durig the Arab Spring.

>>>>

For social cohesion and count of all events, there is a consistent period of above or nearly above chance determinism from the 26th through 46th window (Figure 16). Determinism also shows above or nearly above chance values in window spans 11-16 and 35-37 (Figure 17). For social cohesion and count of positive events, there is a downward trend in RR as the window moves (Figure 18) and determinism stays largely within chance with the exception of windows 13-19. For social cohesion and negative events, there appears to be an extended time period where RR (Figure 11) and DET (Figure 12) were greater than chance, from the 35th through 46th windows. These windows span from May 3rd, 2012 to May 14th, 2012.

@@

### Syria as Source and Target
By adding Syria as a source in the data filtering, the dataset increased in size by 1,690 samples. These additional observations are times where Syria initiated an event with another country. Events initiated by Syria but directed internally within the country were already captured by the target only filtering. The increase in coupling between positive events and social cohesion is thus due to the inclusion of these externally directed events. Though CRQA metrics for count of all and count of negative events with social cohesion were largely unaffected, count of positive events and social cohesion showed significant levels of determinism, number of lines, max line length, and laminarity that were not present in the target filtered data. Given that the Syria during this time was still under Authoritarian rule, the government may have been initiating more positive external events to prevent intervention by other countries or try to cover up what was going on. We believe that the increased coupling of positive events is thus not reflective of actual social cohesion, but happened by chance. The inflation of the number of positive events when including source observations is causing increased coupling, but it is more likely that the Twitter users were using the platform to raise awareness of the violent, internal events that were being inflicted on them by their government officials and armies and not reporting on the positive external events that did not directly affect them or their safety.
By visual inspection of the recurrence plots (RPs; Figures 3-8), there appears to be a shift in the dynamics of these systems around observation 35, or May 3rd, 2012. To further investigate these local dynamics, we performed a sliding window technique known as windowed cross-recurrence quantification analysis (WCRQA).

## Windowed-Recurrence Quantification Analysis
### Syria as Target
The time period of differing dynamics, from observation 38 through 43, appears to be captured by WCRQA of social cohesion and count of negative events for both RR (Figure 13) and DET (Figure 14). The amount of recurrence and determinism for these periods almost consistently lie above chance, suggesting that the intensity of negative events coincide with the degree of social cohesion found on Twitter, and that these states carry across multiple days in a way that is different from that of chance.
The above-chance levels of determinism and recurrence rate are demonstrating the coupling of social cohesion and counts of all and negative events during times of strife. We can see this string of highly violent events reflected in the mode ICEWS event for each day (Figure 15), where from May 1st, 2020 to May 15th, 2020, the most frequently occurring event was almost consistently -10, the most violent event in the coding system. These dates directly correlate with the above chance RR and DET metrics for the WCRQA of social cohesion and count of negative events. Furthermore, for WCRQA of social cohesion and positive event count during this time period, DET (Figure 12) was entirely within chance. This supports our hypothesis, as the positive events are seemingly not coupled with the social cohesion on Twitter during civil uprisings during the Arab Spring.

### 2020-05-27 manuscript.tex
Fix typos in manuscript

By adding Syria as a source in the data filtering, the dataset increased in size by 1,690 samples. These additional observations are times where Syria initiated an event with another country. Events initiated by Syria but directed internally within the country were already captured by the target only filtering. The increase in coupling between positive events and social cohesion is thus due to the inclusion of these externally directed events. Though CRQA metrics for count of all and count of negative events with social cohesion were largely unaffected, count of positive events and social cohesion showed significant levels of determinism, number of lines, max line length, and laminarity that were not present in the target filtered data. Given that the Syria during this time was still under Authoritarian rule, the government may have been initiating more positive external events to prevent intervention by other countries or try to cover up what was going on. We believe that the increased coupling of positive events is thus not reflective of actual social cohesion, but happened by chance. The inflation of the number of positive events when including source observations is causing increased coupling, but it is more likely that the Twitter users were using the platform to raise awareness of the violent, internal events that were being inflicted on them by their government officials and armies and not reporting on the positive external events that did not directly affect them or their saftey.
By visual inspection of the recurrence plots (RPs; Figures 3-8), there appears to be a shift in the dynamics of these systems around observation 35, or May 3rd, 2012. To further investigate these local dynamics, we performed a sliding window technique known as windowed cross-recurrence quantification analysis (WCRQA).

@@

The time period of differing dynamics, from observation 38 through 43, appears to be captured by WCRQA of social cohesion and count of negative events for both RR (Figure 13) and DET (Figure 14). The amount of recurrence and determinism for these periods almost consistently lie above chance, suggesting that the intensity of negative events coincide with the degree of social cohesion found on Twitter, and that these states carry across multiple days in a way that is different from that of chance.
The above-chance levels of determinism and recurrence rate are demonstrating the coupling of social cohesion and counts of all and negative events during times of strife. We can see this string of highly violent events reflected in the mode ICEWS event for each day (Figure 15), where from May 1st, 2020 to May 15th, 2020, the most frequntly occuring event was almost consistently -10, the most violent event in the coding system. These dates directly correlate with the above chance RR and DET metrics for the WCRQA of social cohesion and count of negative events. Furthermore, for WCRQA of social cohesion and positive event count during this time period, DET (Figure 12) was entirely within chance. This supports our hypothesis, as the positive events are seemingly not coupled with the social cohesion on Twitter during civil uprisings durig the Arab Spring.

>>>>

By adding Syria as a source in the data filtering, the dataset increased in size by 1,690 samples. These additional observations are times where Syria initiated an event with another country. Events initiated by Syria but directed internally within the country were already captured by the target only filtering. The increase in coupling between positive events and social cohesion is thus due to the inclusion of these externally directed events. Though CRQA metrics for count of all and count of negative events with social cohesion were largely unaffected, count of positive events and social cohesion showed significant levels of determinism, number of lines, max line length, and laminarity that were not present in the target filtered data. Given that the Syria during this time was still under Authoritarian rule, the government may have been initiating more positive external events to prevent intervention by other countries or try to cover up what was going on. We believe that the increased coupling of positive events is thus not reflective of actual social cohesion, but happened by chance. The inflation of the number of positive events when including source observations is causing increased coupling, but it is more likely that the Twitter users were using the platform to raise awareness of the violent, internal events that were being inflicted on them by their government officials and armies and not reporting on the positive external events that did not directly affect them or their safety.
By visual inspection of the recurrence plots (RPs; Figures 3-8), there appears to be a shift in the dynamics of these systems around observation 35, or May 3rd, 2012. To further investigate these local dynamics, we performed a sliding window technique known as windowed cross-recurrence quantification analysis (WCRQA).

@@

The time period of differing dynamics, from observation 38 through 43, appears to be captured by WCRQA of social cohesion and count of negative events for both RR (Figure 13) and DET (Figure 14). The amount of recurrence and determinism for these periods almost consistently lie above chance, suggesting that the intensity of negative events coincide with the degree of social cohesion found on Twitter, and that these states carry across multiple days in a way that is different from that of chance.
The above-chance levels of determinism and recurrence rate are demonstrating the coupling of social cohesion and counts of all and negative events during times of strife. We can see this string of highly violent events reflected in the mode ICEWS event for each day (Figure 15), where from May 1st, 2020 to May 15th, 2020, the most frequently occurring event was almost consistently -10, the most violent event in the coding system. These dates directly correlate with the above chance RR and DET metrics for the WCRQA of social cohesion and count of negative events. Furthermore, for WCRQA of social cohesion and positive event count during this time period, DET (Figure 12) was entirely within chance. This supports our hypothesis, as the positive events are seemingly not coupled with the social cohesion on Twitter during civil uprisings during the Arab Spring.
